---
title: "Basic Population Genetic Analysis: Analysis Report"
date: "`r Sys.Date()`"
output: html_document
params:
  pca_plot: NULL
  admixture_plot: NULL
  box_ADM: NULL  
  map_ADM: NULL
  manhattan_plot: NULL
---

# Analysis Summary
This report provides a visual summary of the genetic analysis performed, showcasing key insights through PCA, ADMIXTURE, and FST plots. For additional details or questions, please refer to the accompanying data and methods documentation.

## Resume plots
```{r, echo=FALSE, fig.cap="<b>Principal Component Analysis (PCA)</b> providing a visualization of genetic variation between populations or samples. The plot below represents the first two principal components."}
knitr::include_graphics(params$pca_plot)
## Admixture Plot
```{r, echo=FALSE, fig.cap="<b>Admixture plot</b> illustrating the ancestry proportions of individuals across populations. Each bar represents an individual, and the colors indicate the estimated ancestry components."}
knitr::include_graphics(params$admixture_plot)
## Admixture boxplot
```{r, echo=FALSE, fig.cap="<b>Boxplot</b> summarizing the distribution of ancestry proportions for each population."}
knitr::include_graphics(params$box_ADM)
## Admixture mapplot
```{r, echo=FALSE, fig.cap="<b>Map plot</b> showing the geographic distribution of ancestry proportions across populations. Pie charts represent ancestry components at each population location."}
knitr::include_graphics(params$map_ADM)
## FST Plot
```{r, echo=FALSE, fig.cap="<b>Manhattan plot</b> displaying FST values across genomic regions, highlighting regions with significant genetic differentiation between populations."}
knitr::include_graphics(params$manhattan_plot)