---
title: "Analysis Report"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
params:
  pca_plot: NULL
  admixture_plot: NULL
  box_ADM: NULL  
  map_ADM: NULL
  manhattan_plot: NULL
---

# Analysis Summary
This report summarizes the results of the genetic analysis pipeline, including PCA, FST Manhattan, and ADMIXTURE plots.

## Resume plots
```{r, echo=FALSE, fig.cap="The Principal Component Analysis (PCA) provides a visualization of genetic variation between populations or samples. The plot below represents the first two principal components"}
knitr::include_graphics(params$pca_plot)
## Admixture Plot
```{r, echo=FALSE, fig.cap="Admixture Plot"}
knitr::include_graphics(params$admixture_plot)
## Admixture boxplot
```{r, echo=FALSE, fig.cap="box_ADM"}
knitr::include_graphics(params$box_ADM)
## Admixture mapplot
```{r, echo=FALSE, fig.cap="map_ADM"}
knitr::include_graphics(params$map_ADM)
## FST Plot
```{r, echo=FALSE, fig.cap="FST Plot"}
knitr::include_graphics(params$manhattan_plot)